Multi-target detection with application to cryo-electron microscopy

### 2019-02-28 inverse_problems/inverse_problems.tex
.

%Our approach is based on considering the first few entries of the observation's autocorrelations. These entries correspond to products of $y$ with its shifted version, for some small shifts.
%If $s$ would be too clustered, then

As a first setup, we allow any generative model for $s$ which meets the following separation requirement: $s$ is binary, and
\begin{equation}
\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
\label{eq:spacing}
\end{equation}
In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the data.
%Under the separation condition~\eqref{eq:spacing}, we refer to this model as the \emph{homogeneous well-separated model}. 
%In the next section we present a model that alleviates this condition.
%As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas in some cases estimating $x$ is tractable.
Furthermore, we require that the last signal occurrence in $y$ is also followed by at least $L-1$ signal-free (but still noisy) entries.
% This last sentence is required for the proof of the identity of the third-order autocorrelation in Section 3.
This property ensures that correlating $y$ with versions of itself shifted by at most $L-1$ entries does not involve correlating distinct signal occurrences. Once $s$ is determined, for each position $i$ such that $s[i] = 1$, one of the signals $x_k$ is selected independently at random, and accordingly we set $s_k[i] = 1$. As a result, the only properties of $s_1, \ldots, s_K$ that affect the autocorrelations of $y$ are the total number of occurrences of the distinct signals: their individual and relative locations do not intervene.

@@

\TODO{Does the equivalence hold for $\ell\neq 0$?}
\begin{corollary}
	The autocorrelations are equivalent...
\end{corollary}

@@

\begin{proposition} \label{prop:gamma}
	\TODO{Can we do this simultaneously for Poisson? or do we only need to do it for well-separated and invoke the equivalence claim? Not if that claim requires knowledge of $\gamma, \sigma$.}
	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then 
	\begin{equation}
	\gamma  \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
	\end{equation}
\end{proposition}

>>>>

\TODO{The models are not equivalent but related through Corollary~\ref{cor:ac_equivalence}.}
As a first setup, we allow any generative model for $s$ which meets the following separation requirement: $s$ is binary, and
\begin{equation}
\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
\label{eq:spacing}
\end{equation}
In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the data.
%Under the separation condition~\eqref{eq:spacing}, we refer to this model as the \emph{homogeneous well-separated model}. 
%In the next section we present a model that alleviates this condition.
%As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas in some cases estimating $x$ is tractable.
Furthermore, we require that the last signal occurrence in $y$ is also followed by at least $L-1$ signal-free (but still noisy) entries.
% This last sentence is required for the proof of the identity of the third-order autocorrelation in Section 3.
This property ensures that correlating $y$ with versions of itself shifted by at most $L-1$ entries does not involve correlating distinct signal occurrences. Once $s$ is determined, for each position $i$ such that $s[i] = 1$, one of the signals $x_k$ is selected independently at random, and accordingly we set $s_k[i] = 1$. As a result, the only properties of $s_1, \ldots, s_K$ that affect the autocorrelations of $y$ are the total number of occurrences of the distinct signals: their individual and relative locations do not intervene.

@@

\begin{corollary}[informal for now] \label{cor:ac_equivalence}
The first and the second autocorrelations  in the well-separated and the Poisson models are equivalent. 
If $\sigma$ is known, then it is also true for the third-order autocorrelation. If $\sigma$ is unknown, the it is true whenever $\ell_1\neq 0$, $\ell_2\neq 0$ and $\ell_1\neq \ell_2$. 
\end{corollary}

@@

\begin{proposition} \label{prop:gamma}
	\TODO{Can we do this simultaneously for Poisson? or do we only need to do it for well-separated and invoke the equivalence claim? Not if that claim requires knowledge of $\gamma, \sigma$.}
	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then  \TODO{Should remove the limit}
	\begin{equation}
	\gamma  \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
	\end{equation}
\end{proposition}
